Bayesian Sparsification of $\cplx$-valued networks

### 2020-01-30 paper/paper.tex
on log-relevance distribution

% general training strategy
The goal of the following experiments to study the sparsity-performance trade-off of the
proposed Bayesian sparsification methods for $\cplx$-valued networks. To this end we employ
the following training plan in every experiment. The model is trained in three successive
stages:
``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''

@@

During the second stage ``sparsify'' we make the relevant layers bayesian and apply
variational dropout sec.~\ref{ssub:variational_dropout} (or sec.~\ref{ssub:empirical_bayes})
or their $\real$ counterparts. To be able to study the attainable sparsity levels we
inject a coefficient $C \in (0, 1]$ at the KL divergence term in
\eqref{eq:elbo}:
\begin{equation}  \label{eq:elbo_with_coef}
    - \frac{C}N KL(q_{\theta} \| \pi_{\lambda})
    + \frac1{M} \sum_{i=1}^M
        \log p_{\phi}(z_i \mid g(\varepsilon_i; \theta))
    \,. \tag{\ref{eq:elbo}'}
\end{equation}
Increasing $C$ yields increasingly more sparse networks upon termination of this stage.

Before transitioning to the ``fine-tune'' stage we compute the mask of non-zero weights
in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}). Since
the variational approximation factorizes into univariate distributions, whether a $\cplx$
or $\real$ parameter is zero or not is determined from its relevance score $
  \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
$: non-zero (relevant) if $\log \alpha \leq \tau$, zero (irrelevant) otherwise.
In every experiment we set $\tau = -\tfrac12$, which yields extreme levels of sparsity,
especially considering that the recommended setting in \citep{molchanov_variational_2017}
was $3$. The rationale behind our choice was twofold: we use an extra fine tuning
stage, and keep the weights that are away from zero with high probability.

>>>>

% general training strategy
The goal of the following experiments to study the sparsity-performance trade-off of the
proposed Bayesian sparsification methods for $\cplx$-valued networks. To this end we employ
the following training plan in every experiment. The model is trained in three successive
stages: ``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
%
The last two stages are used to compare the .

@@

During the ``sparsify'' stage we make the relevant layers bayesian and apply $\cplx$-variational
dropout sec.~\ref{ssub:variational_dropout} (or sec.~\ref{ssub:empirical_bayes}) or its $\real$
counterpart. To be able to study the attainable sparsity levels we inject a coefficient $
  C \in (0, 1]
$ at the KL divergence term in \eqref{eq:elbo}:
\begin{equation}  \label{eq:elbo_with_coef}
    - \frac{C}N KL(q_{\theta} \| \pi_{\lambda})
    + \frac1{M} \sum_{i=1}^M
        \log p_{\phi}(z_i \mid g(\varepsilon_i; \theta))
    \,. \tag{\ref{eq:elbo}'}
\end{equation}
Higher $C$ yields increasingly more sparse layers upon termination of this stage.

Before transitioning to the ``fine-tune'' stage we compute the mask of non-zero weights
in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}). Since
the variational approximation factorizes into univariate distributions, whether a $\cplx$
or $\real$ parameter is zero or not is determined from its relevance score $
  \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
$: non-zero (relevant) if $\log \alpha \leq \tau$, zero (irrelevant) otherwise. Figure~%
\ref{fig:typical_log_alpha_distrib} depicts the distribution of $\log \alpha$ values
from \textbf{some run}, which exhibits the typical behaviour we noticed in all experiments
conducted: there always is a single mode within the moderately negative range, and one or
two modes to the right of $0$. The relative mass of each mode changes with $C$ and the
higher the coefficient is, the more mass is shifted to the positive half. However, in every
exepriment the trough between the peaks of the negative mode and the first positive one
is around zero.

Thus, in every experiment we set $\tau = -\tfrac12$, which is admittedly very low, especially
considering that the recommended setting in \citep{molchanov_variational_2017} is $3$. This
yields high levels of sparsity,
The rationale behind our choice was twofold: we use an extra fine tuning
stage, and keep the weights that are away from zero with high probability.
